Gammapy: A Python package for gamma-ray astronomy

### 2023-01-27 src/ms-review.tex
Use gamma-ray like consistently

%% Context : formats
In practice, the data reduction workflow of all \gammaray observatories
is remarkably similar. After data calibration, shower events are reconstructed and
gamma/hadron separation is applied to build lists of \gammaray-like events.
The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
or light curves, taking into account the observatory's specific instrument response functions (IRF).
Once the data is reduced to a list of events, the information is independent of
the data-reduction process, and, eventually, of the detection technique. This implies,
for example, that high-level data from IACTs and WCDs can be represented
with the same data model. The efforts to prototype a format usable by various instruments
converged in the so-called \textit{Data Format for \gammaray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (\gadf). This proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of gamma-like events with their measured quantities
such as energy, incident direction and arrival time and a parametrisation of
the IRFs associated with the event list data. %% where? in the data units of a FITS file.

@@

\section{Gamma-ray Data Analysis}
% CN: gamma-like here, was \gammaray-like in the previous section
\begin{figure*}[h!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		\gammapy sub-package structure and data analysis workflow. The top row
        defines the different levels of data reduction, from lists of gamma-like
        events on the left (DL3), to high-level scientific products products
        (DL5) on the right. The direction of the data flow is illustrated with the
        gray arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%
\label{sec:gammaray-data-analysis}
% This might not be the bast place compared to introduction
The data analysis process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This part of the data reduction sequence, sometimes referred to as low-level analysis,
is usually very specific to a given observation technique and even to a given instrument.

@@

%% CN: except for the figures we never introduced what the DL3 or the Data Level acronym is
%% maybe add (see Fig.~1)
\gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
point spread function and energy dispersion ($E_{\rm disp}$).
In general, they depend on event's detector
geometrical parameters, e.g. the field-of-view location or the event elevation angle. So they might be parametrised as
function of such parameters specific to the instrumental technical.

@@

>>>>

%% Context : formats
In practice, the data reduction workflow of all \gammaray observatories
is remarkably similar. After data calibration, shower events are reconstructed and
gamma/hadron separation is applied to build lists of \gammaray-like events.
The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
or light curves, taking into account the observatory's specific instrument response functions (IRF).
Once the data is reduced to a list of events, the information is independent of
the data-reduction process, and, eventually, of the detection technique. This implies,
for example, that high-level data from IACTs and WCDs can be represented
with the same data model. The efforts to prototype a format usable by various instruments
converged in the so-called \textit{Data Format for \gammaray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (\gadf). This proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of \gammaray-like events with their measured quantities
such as energy, incident direction and arrival time and a parametrisation of
the IRFs associated with the event list data. %% where? in the data units of a FITS file.

@@

\section{Gamma-ray Data Analysis}
\begin{figure*}[h!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		\gammapy sub-package structure and data analysis workflow. The top row
        defines the different levels of data reduction, from lists of \gammaray-like
        events on the left (DL3), to high-level scientific products products
        (DL5) on the right. The direction of the data flow is illustrated with the
        gray arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%
\label{sec:gammaray-data-analysis}
% This might not be the bast place compared to introduction
The data analysis process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This part of the data reduction sequence, sometimes referred to as low-level analysis,
is usually very specific to a given observation technique and even to a given instrument.

@@

%% CN: except for the figures we never introduced what the DL3 or the Data Level acronym is
%% maybe add (see Fig.~1)
\gammaray data at the Data Level 3 (DL3) therefore consist of lists of \gammaray-like events and their
corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
point spread function and energy dispersion ($E_{\rm disp}$).
In general, they depend on event's detector
geometrical parameters, e.g. the field-of-view location or the event elevation angle. So they might be parametrised as
function of such parameters specific to the instrumental technical.

@@

\appendix
